\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-06-19 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates: Revision of Section 4.3

In order to investigate the impact of viscosity ratio on flow behaviour, numerical simulations of fluid displacement were conducted in Hele-shaw cells (\ie parallel flat plates separated by infinitesimal space) following \citet{saffman_1986} work. In this work, he investigated the onset of viscous flow instabilities \citep[following his seminal work in][]{saffman_1958} and the impact of boundary conditions in the problem mathematical formulation and solutions.

Here, 2D simulations were conducted in a 5$\times$5 unit-length domain (Fig.~\ref{fig:homoheleshaw}a) fully saturated with a fluid. Wetting phase fluid is driven from the bottom left-hand corner of the domain with velocity of $\frac{\sqrt{2}}{2}$. Newmann boundary condition (\ie, no flux) was imposed to all borders of the domain except at the top right-hand corner (named as sink). Viscosity ratios for this set of simulations are 3 and 10.

>>>>

In order to investigate the impact of viscosity ratio on flow behaviour, numerical simulations of fluid displacement were conducted in Hele-shaw cells (\ie parallel flat plates separated by infinitesimal space) following work by \citet{saffman_1986}. In this manuscript, he investigated the onset of viscous flow instabilities \citep[following his seminal work in][]{saffman_1958} and the impact of boundary conditions in the problem mathematical formulation and solutions.

Here, 2D simulations were conducted in a 5$\times$5 unit-length domain (Fig.~\ref{fig:homoheleshaw}a) fully saturated with a fluid. Wetting phase fluid is driven from the bottom left-hand corner of the domain with velocity of $\frac{\sqrt{2}}{2}$. Newmann boundary condition (\ie no flux) was imposed to all borders of the domain except at the top right-hand corner (named as sink). Viscosity ratios for this set of simulations are 3 and 10.
